---
title: "1-Reading in Data"
output: html_notebook
---

##Structure of the code
The code contains two parts: Part A which works only with one specific dataframe to divide it up by factored or unfactored, and Part B that works with two dataframes - the factored and unfactored version.

For example, Part A would contain only the Argentina dataframe, with columns specified by factored/unfactored. Whereas Part B would have something along the lines of argentina_factored and argentina_unfactored, where each dataframe is EITHER factored or unfactored, not both.

Some functions are repeated in both sections so that you don't have to jump back and forth across parts if you are only trying to look at one.

Suggested order to follow:
1-Reading in Data

#Libraries
```{r, message=FALSE}
library(labelled)
library(sjmisc)
library(tidyr)
library(tidyverse)
library(dplyr)
library(haven)
```


#PART A
Creating factored and unfactored dataframes
```{r}
factor_country <- function(country){
  #Reads file for the country
  country <- read_dta(country)
  #Factors all the columns
  country <- as_factor(country)
  
  #Starts list x
  x <- 1
  
  #Changes name of column to add "factor"
  while(x <= length(country)){
    colnames(country)[x] <- paste(colnames(country)[x], "factor", sep = "-")
    x <- x + 1
  }
  country
}
```

# Creating factored dataframes using `factor_country`
```{r}
panama_factor <- factor_country("1909860951Panama LAPOP merge 2004-2014 v3.0_W_dta.zip")
argentina_factor <- factor_country("1326054827Argentina LAPOP merge 2008-2014 v3.0_W_dta.zip")
bolivia_factor <- factor_country("1500779614Bolivia LAPOP merge 2004-2014 v3.0_W_dta.zip")
brazil_factor <- factor_country("1058457654Brazil LAPOP merge 2007-2014 v3.0_W_dta.zip")
belize_factor <- factor_country("1866361808Belize LAPOP merge 2008-2014 v3.0_W_dta.zip")
canada_factor <- factor_country("257165704Canada LAPOP merge 2006-2014 v3.0_W_dta.zip")
chile_factor <- factor_country("1651690880Chile LAPOP merge 2006-2014 v3.0_W_dta.zip")
colombia_factor <- factor_country("26761406Colombia LAPOP merge 2004-2014 v3.0_W_dta.zip")
costa_factor <- factor_country("312640706CostaRica LAPOP merge 2004-2014 v3.0_W_dta.zip")
ecuador_factor <- factor_country("1562314955Ecuador LAPOP merge 2004-2014 v3.0_W_dta.zip")
elsalvador_factor <- factor_country("71618678ElSalvador LAPOP merge 2004-2014 v3.0_W_dta.zip")
guatemala_factor <- factor_country("833541857Guatemala LAPOP merge 2004-2014 v3.0_W_dta.zip")
guyana_factor <- factor_country("1293237393Guyana LAPOP merge 2006-2014 v3.0_W_dta.zip")
paraguay_factor <- factor_country("450650714Paraguay LAPOP merge 2006-2014 v3.0_W_dta.zip")
honduras_factor <- factor_country("125162980Honduras LAPOP merge 2004-2014 v3.0_W_dta.zip")
jamaica_factor <- factor_country("1518553693Jamaica LAPOP merge 2006-2014 v3.0_W_dta.zip")
mexico_factor <- factor_country("1467358429Mexico LAPOP merge 2004-2014 v3.0_W_dta.zip")
nicaragua_factor <- factor_country("420919900Nicaragua LAPOP merge 2004-2014 v3.0_W_dta.zip")
peru_factor <- factor_country("897206140Peru LAPOP merge 2006-2014 v3.0_W_dta.zip")
suriname_factor <- factor_country("2028239474Suriname LAPOP merge 2010-2014 v3.0_W_dta.zip")
usa_factor <- factor_country("1355754260UnitedStates LAPOP merge 2006-2014 v3.0_W_dta.zip")
uruguay_factor <- factor_country("1222977998Uruguay LAPOP merge 2007-2014 v3.0_W_dta.zip")
venezuela_factor <- factor_country("1165310382Venezuela LAPOP merge 2007-2014 v3.0_W_dta.zip")
```

# Creating unfactored dataframes using `read_dta`
```{r}
panama_unfactor <- read_dta("1909860951Panama LAPOP merge 2004-2014 v3.0_W_dta.zip")
argentina_unfactor <- read_dta("1326054827Argentina LAPOP merge 2008-2014 v3.0_W_dta.zip")
bolivia_unfactor <- read_dta("1500779614Bolivia LAPOP merge 2004-2014 v3.0_W_dta.zip")
brazil_unfactor <- read_dta("1058457654Brazil LAPOP merge 2007-2014 v3.0_W_dta.zip")
belize_unfactor <- read_dta("1866361808Belize LAPOP merge 2008-2014 v3.0_W_dta.zip")
canada_unfactor <- read_dta("257165704Canada LAPOP merge 2006-2014 v3.0_W_dta.zip")
chile_unfactor <- read_dta("1651690880Chile LAPOP merge 2006-2014 v3.0_W_dta.zip")
colombia_unfactor <- read_dta("26761406Colombia LAPOP merge 2004-2014 v3.0_W_dta.zip")
costa_unfactor <- read_dta("312640706CostaRica LAPOP merge 2004-2014 v3.0_W_dta.zip")
ecuador_unfactor <- read_dta("1562314955Ecuador LAPOP merge 2004-2014 v3.0_W_dta.zip")
elsalvador_unfactor <- read_dta("71618678ElSalvador LAPOP merge 2004-2014 v3.0_W_dta.zip")
guatemala_unfactor <- read_dta("833541857Guatemala LAPOP merge 2004-2014 v3.0_W_dta.zip")
guyana_unfactor <- read_dta("1293237393Guyana LAPOP merge 2006-2014 v3.0_W_dta.zip")
paraguay_unfactor <- read_dta("450650714Paraguay LAPOP merge 2006-2014 v3.0_W_dta.zip")
honduras_unfactor <- read_dta("125162980Honduras LAPOP merge 2004-2014 v3.0_W_dta.zip")
jamaica_unfactor <- read_dta("1518553693Jamaica LAPOP merge 2006-2014 v3.0_W_dta.zip")
mexico_unfactor <- read_dta("1467358429Mexico LAPOP merge 2004-2014 v3.0_W_dta.zip")
nicaragua_unfactor <- read_dta("420919900Nicaragua LAPOP merge 2004-2014 v3.0_W_dta.zip")
peru_unfactor <- read_dta("897206140Peru LAPOP merge 2006-2014 v3.0_W_dta.zip")
suriname_unfactor <- read_dta("2028239474Suriname LAPOP merge 2010-2014 v3.0_W_dta.zip")
usa_unfactor <- read_dta("1355754260UnitedStates LAPOP merge 2006-2014 v3.0_W_dta.zip")
uruguay_unfactor <- read_dta("1222977998Uruguay LAPOP merge 2007-2014 v3.0_W_dta.zip")
venezuela_unfactor <- read_dta("1165310382Venezuela LAPOP merge 2007-2014 v3.0_W_dta.zip")
```


# Creating factored dataframes of 2016/17 questionnaires using `factor_country`
```{r}
argentina_16_factor <- factor_country("42076439Argentina LAPOP AmericasBarometer 2017 V1.0_W.dta")
venezuela_16_factor  <- factor_country("25258094Venezuela LAPOP AmericasBarometer 2016-17 V1.0_W.dta")
bolivia_16_factor  <- factor_country("142790203Bolivia LAPOP AmericasBarometer 2017 V1.0_W.dta")
brazil_16_factor  <- factor_country("780314464Brazil LAPOP AmericasBarometer 2017 V1.0_W.dta")
canada_16_factor  <- factor_country("576555173Canada LAPOP AmericasBarometer 2017 V1.0_W.dta")
chile_16_factor  <- factor_country("336280178Chile LAPOP AmericasBarometer 2017 V1.0_W.dta")
colombia_16_factor  <- factor_country("1966987763Colombia LAPOP AmericasBarometer 2016 V1.0_W.dta")
costa_16_factor  <- factor_country("1636511905CostaRica LAPOP AmericasBarometer 2016 V1.0_W.dta")
ecuador_16_factor  <- factor_country("1061044693Ecuador LAPOP AmericasBarometer 2016-17 V1.0_W.dta")
elsalvador_16_factor  <- factor_country("381267663ElSalvador LAPOP AmericasBarometer 2016 V1.0_W.dta")
guatemala_16_factor  <- factor_country("823416394Guatemala LAPOP AmericasBarometer 2017 V1.0_W.dta")
guyana_16_factor  <- factor_country("1740874324Guyana LAPOP AmericasBarometer 2016 V1.0_W.dta")
honduras_16_factor  <- factor_country("1252173714Honduras LAPOP AmericasBarometer 2016 V1.0_W.dta")
jamaica_16_factor  <- factor_country("428805428Jamaica LAPOP AmericasBarometer 2017 V1.0_W.dta")
mexico_16_factor  <- factor_country("275973272Mexico LAPOP AmericasBarometer 2017 V1.0_W.dta")
nicaragua_16_factor  <- factor_country("1862548546Nicaragua LAPOP AmericasBarometer 2016 V1.0_W.dta")
panama_16_factor  <- factor_country("2078678947Panama LAPOP AmericasBarometer 2017 V1.0_W.dta")
paraguay_16_factor <- factor_country("1311870907Paraguay LAPOP AmericasBarometer 2016 V1.0 W.dta")
peru_16_factor  <- factor_country("83639715Peru_LAPOP_AmericasBarometer_2017_V1.1_W.dta")
usa_16_factor  <- factor_country("2133069031United States LAPOP AmericasBarometer 2017 V1.0_W.dta")
uruguay_16_factor  <- factor_country("646644681Uruguay LAPOP AmericasBarometer 2017 V1.0_W.dta")
```


# Creating unfactored dataframes of 2016/17 questionnaires using `read_dta`
```{r}
argentina_16_unfactor <- read_dta("42076439Argentina LAPOP AmericasBarometer 2017 V1.0_W.dta")
venezuela_16_unfactor  <- read_dta("25258094Venezuela LAPOP AmericasBarometer 2016-17 V1.0_W.dta")
bolivia_16_unfactor  <- read_dta("142790203Bolivia LAPOP AmericasBarometer 2017 V1.0_W.dta")
brazil_16_unfactor  <- read_dta("780314464Brazil LAPOP AmericasBarometer 2017 V1.0_W.dta")
canada_16_unfactor  <- read_dta("576555173Canada LAPOP AmericasBarometer 2017 V1.0_W.dta")
chile_16_unfactor  <- read_dta("336280178Chile LAPOP AmericasBarometer 2017 V1.0_W.dta")
colombia_16_unfactor  <- read_dta("1966987763Colombia LAPOP AmericasBarometer 2016 V1.0_W.dta")
costa_16_unfactor  <- read_dta("1636511905CostaRica LAPOP AmericasBarometer 2016 V1.0_W.dta")
ecuador_16_unfactor  <- read_dta("1061044693Ecuador LAPOP AmericasBarometer 2016-17 V1.0_W.dta")
elsalvador_16_unfactor  <- read_dta("381267663ElSalvador LAPOP AmericasBarometer 2016 V1.0_W.dta")
guatemala_16_unfactor  <- read_dta("823416394Guatemala LAPOP AmericasBarometer 2017 V1.0_W.dta")
guyana_16_unfactor  <- read_dta("1740874324Guyana LAPOP AmericasBarometer 2016 V1.0_W.dta")
honduras_16_unfactor  <- read_dta("1252173714Honduras LAPOP AmericasBarometer 2016 V1.0_W.dta")
jamaica_16_unfactor  <- read_dta("428805428Jamaica LAPOP AmericasBarometer 2017 V1.0_W.dta")
mexico_16_unfactor  <- read_dta("275973272Mexico LAPOP AmericasBarometer 2017 V1.0_W.dta")
nicaragua_16_unfactor  <- read_dta("1862548546Nicaragua LAPOP AmericasBarometer 2016 V1.0_W.dta")
panama_16_unfactor  <- read_dta("2078678947Panama LAPOP AmericasBarometer 2017 V1.0_W.dta")
paraguay_16_unfactor <- read_dta("1311870907Paraguay LAPOP AmericasBarometer 2016 V1.0 W.dta")
peru_16_unfactor  <- read_dta("83639715Peru_LAPOP_AmericasBarometer_2017_V1.1_W.dta")
usa_16_unfactor  <- read_dta("2133069031United States LAPOP AmericasBarometer 2017 V1.0_W.dta")
uruguay_16_unfactor  <- read_dta("646644681Uruguay LAPOP AmericasBarometer 2017 V1.0_W.dta")
```

#For Reference only: Alternate
Step 1 - read in the data
Step 2 - split it up into what needs to be factored vs what doesn't
Step 3 - return the new data set of the combined unfactored and factored version
```{r}
#Function used to factor the entire data frame
factor_country <- function(country) {
  country_factor <- as_factor(country)
  return(country_factor)
}

#Makes a list that will store column names that need to be factored
factor <- rep(NA, 900)
i <- 1
x <- 1

#Makes a list of columns that should be factored then makes dataframe of columns that should remain unfactored
factor_unfactor_combine <- function(filename){
  #Reads in the data
  country <- read_dta(filename)
  #Makes a list of all the columns that are present in the country
  columns <- attributes(country)$names
  #Creates a dataframe that the unfactored data can be held in
  unfactor <- data_frame('extra' = country$pais)
  
  #Factored version of the country
  pais <- as_factor(country %>%
                      select(pais))
  #Removes Pais column
  country <- country %>%
    select(-pais)
  #Combines country and pais
  country <- cbind(country, pais)
  
  #Loops through each of the columns, determining if it needs to be factored or not
  while(x <= length(columns)){
    #Stores one of the columns in d, have to use !!! syms because columns is in a string list format
    d <- (country %>%
            select(!!! syms(columns[x])))
    #If 6,7,8,9, or 10 are in d
    if((6 %in% d[[unlist(columns[x])]] || 7 %in% d[[unlist(columns[x])]] || 8 %in% d[[unlist(columns[x])]] || 9 %in% d[[unlist(columns[x])]] || 10 %in% d[[unlist(columns[x])]])){
      #If it is, then add to the dataframe created earlier
      unfactor <- cbind(unfactor, d)
    } else{
      #If it isn't, then add the column name to the factor list
      factor[i] <- unlist(columns[x])
      i <- i + 1
    }
    x <-  x + 1
  }
  
  #Remove "extra", the column originally used to create the dataframe
  unfactor <- unfactor %>%
    select(-extra)
  #Select the columns that should be factored, shrink country down to just those columns and factor it
  factor <- factor[!is.na(factor)]
  country <- country[factor]
  factored_country <- factor_country(country)
  #Combine unfactored and factored together
  full_country <- cbind(factored_country, unfactor)
  
  return(full_country)
}
```


#Applying `factor_unfactor_combine()` to all countries
```{r}
panama <- factor_unfactor_combine("1909860951Panama LAPOP merge 2004-2014 v3.0_W_dta.zip")
argentina <- factor_unfactor_combine("1326054827Argentina LAPOP merge 2008-2014 v3.0_W_dta.zip")
bolivia <- factor_unfactor_combine("1500779614Bolivia LAPOP merge 2004-2014 v3.0_W_dta.zip")
brazil <- factor_unfactor_combine("1058457654Brazil LAPOP merge 2007-2014 v3.0_W_dta.zip")
belize <- factor_unfactor_combine("1866361808Belize LAPOP merge 2008-2014 v3.0_W_dta.zip")
canada <- factor_unfactor_combine("257165704Canada LAPOP merge 2006-2014 v3.0_W_dta.zip")
chile <- factor_unfactor_combine("1651690880Chile LAPOP merge 2006-2014 v3.0_W_dta.zip")
colombia <- factor_unfactor_combine("26761406Colombia LAPOP merge 2004-2014 v3.0_W_dta.zip")
costa <- factor_unfactor_combine("312640706CostaRica LAPOP merge 2004-2014 v3.0_W_dta.zip")
ecuador <- factor_unfactor_combine("1562314955Ecuador LAPOP merge 2004-2014 v3.0_W_dta.zip")
elsalvador <- factor_unfactor_combine("71618678ElSalvador LAPOP merge 2004-2014 v3.0_W_dta.zip")
guatemala <- factor_unfactor_combine("833541857Guatemala LAPOP merge 2004-2014 v3.0_W_dta.zip")
guyana <- factor_unfactor_combine("1293237393Guyana LAPOP merge 2006-2014 v3.0_W_dta.zip")
paraguay <- factor_unfactor_combine("450650714Paraguay LAPOP merge 2006-2014 v3.0_W_dta.zip")
honduras <- factor_unfactor_combine("125162980Honduras LAPOP merge 2004-2014 v3.0_W_dta.zip")
jamaica <- factor_unfactor_combine("1518553693Jamaica LAPOP merge 2006-2014 v3.0_W_dta.zip")
mexico <- factor_unfactor_combine("1467358429Mexico LAPOP merge 2004-2014 v3.0_W_dta.zip")
nicaragua <- factor_unfactor_combine("420919900Nicaragua LAPOP merge 2004-2014 v3.0_W_dta.zip")
peru <- factor_unfactor_combine("897206140Peru LAPOP merge 2006-2014 v3.0_W_dta.zip")
suriname <- factor_unfactor_combine("2028239474Suriname LAPOP merge 2010-2014 v3.0_W_dta.zip")
usa <- factor_unfactor_combine("1355754260UnitedStates LAPOP merge 2006-2014 v3.0_W_dta.zip")
uruguay <- factor_unfactor_combine("1222977998Uruguay LAPOP merge 2007-2014 v3.0_W_dta.zip")
venezuela <- factor_unfactor_combine("1165310382Venezuela LAPOP merge 2007-2014 v3.0_W_dta.zip")
```

