---
title: "1-Reading in Data"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

# Overall Structure of the code
Include a brief sentence with a summary of code structure.
- Divided by merged and 16/17

Suggested order to follow:
1. Reading in Data
2. Categories and Questions
3. Adding Wave Column
4. Creating Unique ID

## Libraries
```{r, message=FALSE}
library(labelled)
library(sjmisc)
library(tidyr)
library(tidyverse)
library(dplyr)
library(haven)
library(assertr)
```


## Creating factored and unfactored dataframes
```{r}
factor_country <- function(country){
  #Reads file for the country
  country <- read_dta(country)
  #Factors all the columns
  country <- as_factor(country)
  
  #Starts list x
  x <- 1
  
  #Changes name of column to add "factor"
  while(x <= length(country)){
      colnames(country)[x] <- paste(colnames(country)[x], "factor", sep = "_")
     x <- x + 1
  }
  country
}
```

# Reading in merged country files
## Creating factored dataframes using `factor_country`
```{r}
panama_factor <- factor_country("1909860951Panama LAPOP merge 2004-2014 v3.0_W_dta.zip")
argentina_factor <- factor_country("1326054827Argentina LAPOP merge 2008-2014 v3.0_W_dta.zip")
bolivia_factor <- factor_country("1500779614Bolivia LAPOP merge 2004-2014 v3.0_W_dta.zip")
brazil_factor <- factor_country("1058457654Brazil LAPOP merge 2007-2014 v3.0_W_dta.zip")
belize_factor <- factor_country("1866361808Belize LAPOP merge 2008-2014 v3.0_W_dta.zip")
canada_factor <- factor_country("257165704Canada LAPOP merge 2006-2014 v3.0_W_dta.zip")
chile_factor <- factor_country("1651690880Chile LAPOP merge 2006-2014 v3.0_W_dta.zip")
colombia_factor <- factor_country("26761406Colombia LAPOP merge 2004-2014 v3.0_W_dta.zip")
costa_factor <- factor_country("312640706CostaRica LAPOP merge 2004-2014 v3.0_W_dta.zip")
ecuador_factor <- factor_country("1562314955Ecuador LAPOP merge 2004-2014 v3.0_W_dta.zip")
elsalvador_factor <- factor_country("71618678ElSalvador LAPOP merge 2004-2014 v3.0_W_dta.zip")
guatemala_factor <- factor_country("833541857Guatemala LAPOP merge 2004-2014 v3.0_W_dta.zip")
guyana_factor <- factor_country("1293237393Guyana LAPOP merge 2006-2014 v3.0_W_dta.zip")
paraguay_factor <- factor_country("450650714Paraguay LAPOP merge 2006-2014 v3.0_W_dta.zip")
honduras_factor <- factor_country("125162980Honduras LAPOP merge 2004-2014 v3.0_W_dta.zip")
jamaica_factor <- factor_country("1518553693Jamaica LAPOP merge 2006-2014 v3.0_W_dta.zip")
mexico_factor <- factor_country("1467358429Mexico LAPOP merge 2004-2014 v3.0_W_dta.zip")
nicaragua_factor <- factor_country("420919900Nicaragua LAPOP merge 2004-2014 v3.0_W_dta.zip")
peru_factor <- factor_country("897206140Peru LAPOP merge 2006-2014 v3.0_W_dta.zip")
suriname_factor <- factor_country("2028239474Suriname LAPOP merge 2010-2014 v3.0_W_dta.zip")
usa_factor <- factor_country("1355754260UnitedStates LAPOP merge 2006-2014 v3.0_W_dta.zip")
uruguay_factor <- factor_country("1222977998Uruguay LAPOP merge 2007-2014 v3.0_W_dta.zip")
venezuela_factor <- factor_country("1165310382Venezuela LAPOP merge 2007-2014 v3.0_W_dta.zip")
```

## Creating unfactored dataframes using `read_dta`
```{r}
panama_unfactor <- read_dta("1909860951Panama LAPOP merge 2004-2014 v3.0_W_dta.zip")
argentina_unfactor <- read_dta("1326054827Argentina LAPOP merge 2008-2014 v3.0_W_dta.zip")
bolivia_unfactor <- read_dta("1500779614Bolivia LAPOP merge 2004-2014 v3.0_W_dta.zip")
brazil_unfactor <- read_dta("1058457654Brazil LAPOP merge 2007-2014 v3.0_W_dta.zip")
belize_unfactor <- read_dta("1866361808Belize LAPOP merge 2008-2014 v3.0_W_dta.zip")
canada_unfactor <- read_dta("257165704Canada LAPOP merge 2006-2014 v3.0_W_dta.zip")
chile_unfactor <- read_dta("1651690880Chile LAPOP merge 2006-2014 v3.0_W_dta.zip")
colombia_unfactor <- read_dta("26761406Colombia LAPOP merge 2004-2014 v3.0_W_dta.zip")
costa_unfactor <- read_dta("312640706CostaRica LAPOP merge 2004-2014 v3.0_W_dta.zip")
ecuador_unfactor <- read_dta("1562314955Ecuador LAPOP merge 2004-2014 v3.0_W_dta.zip")
elsalvador_unfactor <- read_dta("71618678ElSalvador LAPOP merge 2004-2014 v3.0_W_dta.zip")
guatemala_unfactor <- read_dta("833541857Guatemala LAPOP merge 2004-2014 v3.0_W_dta.zip")
guyana_unfactor <- read_dta("1293237393Guyana LAPOP merge 2006-2014 v3.0_W_dta.zip")
paraguay_unfactor <- read_dta("450650714Paraguay LAPOP merge 2006-2014 v3.0_W_dta.zip")
honduras_unfactor <- read_dta("125162980Honduras LAPOP merge 2004-2014 v3.0_W_dta.zip")
jamaica_unfactor <- read_dta("1518553693Jamaica LAPOP merge 2006-2014 v3.0_W_dta.zip")
mexico_unfactor <- read_dta("1467358429Mexico LAPOP merge 2004-2014 v3.0_W_dta.zip")
nicaragua_unfactor <- read_dta("420919900Nicaragua LAPOP merge 2004-2014 v3.0_W_dta.zip")
peru_unfactor <- read_dta("897206140Peru LAPOP merge 2006-2014 v3.0_W_dta.zip")
suriname_unfactor <- read_dta("2028239474Suriname LAPOP merge 2010-2014 v3.0_W_dta.zip")
usa_unfactor <- read_dta("1355754260UnitedStates LAPOP merge 2006-2014 v3.0_W_dta.zip")
uruguay_unfactor <- read_dta("1222977998Uruguay LAPOP merge 2007-2014 v3.0_W_dta.zip")
venezuela_unfactor <- read_dta("1165310382Venezuela LAPOP merge 2007-2014 v3.0_W_dta.zip")
```



# Reading in 2016/17 files
## Creating factored dataframes of 2016/17 questionnaires using `factor_country`
```{r}
argentina_16_factor <- factor_country("/Users/lindsayhardy/Clean-LAPOP/42076439Argentina LAPOP AmericasBarometer 2017 V1.0_W (1).dta")
venezuela_16_factor  <- factor_country("25258094Venezuela LAPOP AmericasBarometer 2016-17 V1.0_W.dta")
bolivia_16_factor  <- factor_country("142790203Bolivia LAPOP AmericasBarometer 2017 V1.0_W.dta")
brazil_16_factor  <- factor_country("780314464Brazil LAPOP AmericasBarometer 2017 V1.0_W.dta")
canada_16_factor  <- factor_country("576555173Canada LAPOP AmericasBarometer 2017 V1.0_W.dta")
chile_16_factor  <- factor_country("336280178Chile LAPOP AmericasBarometer 2017 V1.0_W.dta")
colombia_16_factor  <- factor_country("1966987763Colombia LAPOP AmericasBarometer 2016 V1.0_W.dta")
costa_16_factor  <- factor_country("1636511905CostaRica LAPOP AmericasBarometer 2016 V1.0_W.dta")
ecuador_16_factor  <- factor_country("1061044693Ecuador LAPOP AmericasBarometer 2016-17 V1.0_W.dta")
elsalvador_16_factor  <- factor_country("381267663ElSalvador LAPOP AmericasBarometer 2016 V1.0_W.dta")
guatemala_16_factor  <- factor_country("823416394Guatemala LAPOP AmericasBarometer 2017 V1.0_W.dta")
guyana_16_factor  <- factor_country("1740874324Guyana LAPOP AmericasBarometer 2016 V1.0_W.dta")
honduras_16_factor  <- factor_country("1252173714Honduras LAPOP AmericasBarometer 2016 V1.0_W.dta")
jamaica_16_factor  <- factor_country("428805428Jamaica LAPOP AmericasBarometer 2017 V1.0_W.dta")
mexico_16_factor  <- factor_country("275973272Mexico LAPOP AmericasBarometer 2017 V1.0_W.dta")
nicaragua_16_factor  <- factor_country("1862548546Nicaragua LAPOP AmericasBarometer 2016 V1.0_W.dta")
panama_16_factor  <- factor_country("2078678947Panama LAPOP AmericasBarometer 2017 V1.0_W.dta")
paraguay_16_factor <- factor_country("1311870907Paraguay LAPOP AmericasBarometer 2016 V1.0 W.dta")
peru_16_factor  <- factor_country("83639715Peru_LAPOP_AmericasBarometer_2017_V1.1_W.dta")
usa_16_factor  <- factor_country("2133069031United States LAPOP AmericasBarometer 2017 V1.0_W.dta")
uruguay_16_factor  <- factor_country("646644681Uruguay LAPOP AmericasBarometer 2017 V1.0_W.dta")
```


## Creating unfactored dataframes of 2016/17 questionnaires using `read_dta`
```{r}
argentina_16_unfactor <- read_dta("/Users/lindsayhardy/Clean-LAPOP/42076439Argentina LAPOP AmericasBarometer 2017 V1.0_W (1).dta") %>%
  transform(uniq_id = as.character(uniq_id))

venezuela_16_unfactor  <- read_dta("25258094Venezuela LAPOP AmericasBarometer 2016-17 V1.0_W.dta") %>% 
  transform(uniq_id = as.character(uniq_id))

bolivia_16_unfactor  <- read_dta("142790203Bolivia LAPOP AmericasBarometer 2017 V1.0_W.dta") %>% 
  transform(uniq_id = as.character(uniq_id))

brazil_16_unfactor  <- read_dta("780314464Brazil LAPOP AmericasBarometer 2017 V1.0_W.dta") %>% 
  transform(uniq_id = as.character(uniq_id))

canada_16_unfactor  <- read_dta("576555173Canada LAPOP AmericasBarometer 2017 V1.0_W.dta") %>% 
  transform(uniq_id = as.character(uniq_id))

chile_16_unfactor  <- read_dta("336280178Chile LAPOP AmericasBarometer 2017 V1.0_W.dta") %>% 
  transform(uniq_id = as.character(uniq_id))

colombia_16_unfactor  <- read_dta("1966987763Colombia LAPOP AmericasBarometer 2016 V1.0_W.dta") %>% 
  transform(uniq_id = as.character(uniq_id))

costa_16_unfactor  <- read_dta("1636511905CostaRica LAPOP AmericasBarometer 2016 V1.0_W.dta") %>% 
  transform(uniq_id = as.character(uniq_id))

ecuador_16_unfactor  <- read_dta("1061044693Ecuador LAPOP AmericasBarometer 2016-17 V1.0_W.dta") %>% 
  transform(uniq_id = as.character(uniq_id))

elsalvador_16_unfactor  <- read_dta("381267663ElSalvador LAPOP AmericasBarometer 2016 V1.0_W.dta") %>% 
  transform(uniq_id = as.character(uniq_id))

guatemala_16_unfactor  <- read_dta("823416394Guatemala LAPOP AmericasBarometer 2017 V1.0_W.dta") %>% 
  transform(uniq_id = as.character(uniq_id))

guyana_16_unfactor  <- read_dta("1740874324Guyana LAPOP AmericasBarometer 2016 V1.0_W.dta") %>% 
  transform(uniq_id = as.character(uniq_id))

honduras_16_unfactor  <- read_dta("1252173714Honduras LAPOP AmericasBarometer 2016 V1.0_W.dta") %>% 
  transform(uniq_id = as.character(uniq_id))

jamaica_16_unfactor  <- read_dta("428805428Jamaica LAPOP AmericasBarometer 2017 V1.0_W.dta") %>% 
  transform(uniq_id = as.character(uniq_id))

mexico_16_unfactor  <- read_dta("275973272Mexico LAPOP AmericasBarometer 2017 V1.0_W.dta") %>% 
  transform(uniq_id = as.character(uniq_id))

nicaragua_16_unfactor  <- read_dta("1862548546Nicaragua LAPOP AmericasBarometer 2016 V1.0_W.dta") %>% 
  transform(uniq_id = as.character(uniq_id))

panama_16_unfactor  <- read_dta("2078678947Panama LAPOP AmericasBarometer 2017 V1.0_W.dta") %>% 
  transform(uniq_id = as.character(uniq_id))

paraguay_16_unfactor <- read_dta("1311870907Paraguay LAPOP AmericasBarometer 2016 V1.0 W.dta") %>% 
  transform(uniq_id = as.character(uniq_id))

peru_16_unfactor  <- read_dta("83639715Peru_LAPOP_AmericasBarometer_2017_V1.1_W.dta") %>% 
  transform(uniq_id = as.character(uniq_id))

usa_16_unfactor  <- read_dta("2133069031United States LAPOP AmericasBarometer 2017 V1.0_W.dta") %>% 
  transform(uniq_id = as.character(uniq_id))

uruguay_16_unfactor  <- read_dta("646644681Uruguay LAPOP AmericasBarometer 2017 V1.0_W.dta") %>% 
  transform(uniq_id = as.character(uniq_id))
```
