---
title: "2-common columns"
output: html_notebook
---
This finds all the common columns across the countries, and also the common labels/questions across the countries

#PART A
```{r}
same_column_names <- function(country1, country2) {
  #Collects names of each column from their respective data set
  list1 <- attributes(country1)$names 
  list2 <- attributes(country2)$names
  #Initializing list
  firstlist <- vector("list", 800)

  i <- 1
  n <- 0
  k <- 1

  #Looping through both column names to find similarities
  for (name1 in list1) {
    if(name1 %in% list2)  {
        firstlist[[i]] <- name1
        i <- i + 1
      }
  }


  #Getting rid of NULL values
  for(x in firstlist){
    if(is.null(x) == FALSE) {
     n <- n + 1
    }
  }
 
  final <- vector("list", n)

  for(x in firstlist) {
    final[[k]] <- x
    k <- k + 1
  }

  #Print result
  return(final)
}
```


```{r}
list_and_factor <- function(list1, country2) {
  #Collects names of each column from their respective data set
  list2 <- attributes(country2)$names
  #Initializing list
  firstlist <- vector("list", 800)

  i <- 1
  n <- 0
  k <- 1

  #Looping through both column names to find similarities
  for (name1 in list1) {
    if(name1 %in% list2)  {
        firstlist[[i]] <- name1
        i <- i + 1
      }
  }


  #Getting rid of NULL values
  for(x in firstlist){
    if(is.null(x) == FALSE) {
     n <- n + 1
    }
  }
 
  final <- vector("list", n)

  for(x in firstlist) {
    final[[k]] <- x
    k <- k + 1
  }

  #Print result
  return(final)
}
```

```{r}
first <- same_column_names(argentina, bolivia)
second <- list_and_factor(first, brazil)
third <- list_and_factor(second, belize)
fourth <- list_and_factor(third, canada)
fifth <- list_and_factor(fourth, chile)
sixth <- list_and_factor(fifth, colombia)
seven <- list_and_factor(sixth, costa)
eigth <- list_and_factor(seven, ecuador)
nine <- list_and_factor(eigth, elsalvador)
ten <- list_and_factor(nine, guatemala)
eleven <- list_and_factor(ten, guyana)
twelve <- list_and_factor(eleven, paraguay)
thirteen <- list_and_factor(twelve, honduras)
fourteen <- list_and_factor(thirteen, jamaica)
fifteen <- list_and_factor(fourteen, mexico)
sixteen <- list_and_factor(fifteen, nicaragua)
seventeen <- list_and_factor(sixteen, panama)
eighteen <- list_and_factor(seventeen, peru)
nineteen <- list_and_factor(eighteen, suriname)
twenty <- list_and_factor(nineteen, usa)
twen_one <- list_and_factor(twenty, uruguay)
all_common_col <- list_and_factor(twen_one, venezuela)
```


#PART B

```{r}
same_column_names <- function(country1, country2) {
  #Collects names of each column from their respective data set
  list1 <- attributes(country1)$names 
  list2 <- attributes(country2)$names
  #Initializing list
  firstlist <- vector("list", 800)

  i <- 1
  n <- 0
  k <- 1

  #Looping through both column names to find similarities
  for (name1 in list1) {
    if(name1 %in% list2)  {
        firstlist[[i]] <- name1
        i <- i + 1
      }
  }


  #Getting rid of NULL values
  for(x in firstlist){
    if(is.null(x) == FALSE) {
     n <- n + 1
    }
  }
 
  final <- vector("list", n)

  for(x in firstlist) {
    final[[k]] <- x
    k <- k + 1
  }

  #Print result
  return(final)
}
```


```{r}
list_and_factor <- function(list1, country2) {
  #Collects names of each column from their respective data set
  list2 <- attributes(country2)$names
  #Initializing list
  firstlist <- vector("list", 800)

  i <- 1
  n <- 0
  k <- 1

  #Looping through both column names to find similarities
  for (name1 in list1) {
    if(name1 %in% list2)  {
        firstlist[[i]] <- name1
        i <- i + 1
      }
  }


  #Getting rid of NULL values
  for(x in firstlist){
    if(is.null(x) == FALSE) {
     n <- n + 1
    }
  }
 
  final <- vector("list", n)

  for(x in firstlist) {
    final[[k]] <- x
    k <- k + 1
  }

  #Print result
  return(final)
}
```


Unfactored
```{r}
first <- same_column_names(argentina_unfactor, bolivia_unfactor)
second <- list_and_factor(first, brazil_unfactor)
third <- list_and_factor(second, belize_unfactor)
fourth <- list_and_factor(third, canada_unfactor)
fifth <- list_and_factor(fourth, chile_unfactor)
sixth <- list_and_factor(fifth, colombia_unfactor)
seven <- list_and_factor(sixth, costa_unfactor)
eigth <- list_and_factor(seven, ecuador_unfactor)
nine <- list_and_factor(eigth, elsalvador_unfactor)
ten <- list_and_factor(nine, guatemala_unfactor)
eleven <- list_and_factor(ten, guyana_unfactor)
twelve <- list_and_factor(eleven, paraguay_unfactor)
thirteen <- list_and_factor(twelve, honduras_unfactor)
fourteen <- list_and_factor(thirteen, jamaica_unfactor)
fifteen <- list_and_factor(fourteen, mexico_unfactor)
sixteen <- list_and_factor(fifteen, nicaragua_unfactor)
seventeen <- list_and_factor(sixteen, panama_unfactor)
eighteen <- list_and_factor(seventeen, peru_unfactor)
nineteen <- list_and_factor(eighteen, suriname_unfactor)
twenty <- list_and_factor(nineteen, usa_unfactor)
twen_one <- list_and_factor(twenty, uruguay_unfactor)
common_unfactor <- list_and_factor(twen_one, venezuela_unfactor)
```

Factored
```{r}
first <- same_column_names(argentina_factor, bolivia_factor)
second <- list_and_factor(first, brazil_factor)
third <- list_and_factor(second, belize_factor)
fourth <- list_and_factor(third, canada_factor)
fifth <- list_and_factor(fourth, chile_factor)
sixth <- list_and_factor(fifth, colombia_factor)
seven <- list_and_factor(sixth, costa_factor)
eigth <- list_and_factor(seven, ecuador_factor)
nine <- list_and_factor(eigth, elsalvador_factor)
ten <- list_and_factor(nine, guatemala_factor)
eleven <- list_and_factor(ten, guyana_factor)
twelve <- list_and_factor(eleven, paraguay_factor)
thirteen <- list_and_factor(twelve, honduras_factor)
fourteen <- list_and_factor(thirteen, jamaica_factor)
fifteen <- list_and_factor(fourteen, mexico_factor)
sixteen <- list_and_factor(fifteen, nicaragua_factor)
seventeen <- list_and_factor(sixteen, panama_factor)
eighteen <- list_and_factor(seventeen, peru_factor)
nineteen <- list_and_factor(eighteen, suriname_factor)
twenty <- list_and_factor(nineteen, usa_factor)
twen_one <- list_and_factor(twenty, uruguay_factor)
common_factor <- list_and_factor(twen_one, venezuela_factor)
```

#For reference only

Below this is NOT necessary to run, but we wanted to keep it just incase we need it in the future. It makes a unique list of all the common questions that are a part of each of the countries


Need to compare all common questions not just column names, because there are different questions for the column names



```{r}
questions <- function(country){
  i <- 1
  x <- 1
  column <- length(attributes(country)$names)
  new_list <- rep(NA, column)
			  while(i <= length(new_list)){
			    original <- attributes(country)$names[i]
			    new <- attributes(country[[original]])$label
			    if(is.null(new) == FALSE){
			      new_list[x] <- new
			      x <- x + 1
			    }
			    i <- i + 1
			  }
			  new_list
}
```


```{r}
argentina_questions <- questions(argentina)
belize_questions  <- questions(belize)
bolivia_questions  <- questions(bolivia)
brazil_questions  <- questions(brazil)
canada_questions  <- questions(canada)
chile_questions  <- questions(chile)
colombia_questions  <- questions(colombia)
costa_questions <- questions(costa)
ecuador_questions <- questions(ecuador)
elsalvador_questions <- questions(elsalvador)
guatemala_questions <- questions(guatemala)
#guyana_questions <- questions(guyana) #Commented out because it is English-only
honduras_questions <- questions(honduras)
#jamaica_questions <- questions(jamaica) #Commented out because it is English-only
mexico_questions <- questions(mexico)
nicaragua_questions <- questions(nicaragua)
panama_questions <- questions(panama)
paraguay_questions <- questions(paraguay)
peru_questions <- questions(peru)
suriname_questions <- questions(suriname)
usa_questions <- questions(usa)
uruguay_questions <- questions(uruguay)
venezuela_questions <- questions(venezuela)
```


Comparing all lists together 

```{r}
list_and_list <- function(country1, country2) {
  #Collects names of each column from their respective data set
  first <- country1
  second <- country2
	  
			  
  #Initializing list
  firstlist <- vector("list", 800)
  l <- vector("list", 25)

  i <- 1
  n <- 0
  k <- 1
  x <- 1

  #Looping through both column names to find similarities
  for (name1 in first) {
      if (name1 %in% second) {
        firstlist[[i]] <- name1
        i <- i + 1
      }
  }


  #Getting rid of NULL values
  for(x in firstlist){
    if(is.null(x) == FALSE) {
     n <- n + 1
    }
  }
 
  final <- vector("list", n)

  for(x in firstlist) {
    final[[k]] <- x
    k <- k + 1
  }

  #Print result
  return(final)
}
```

```{r}
firstlist <- vector("list", 800)
l <- vector("list", 25)

  i <- 1
  n <- 0
  k <- 1
  x <- 1

  #Looping through both column names to find similarities
  for (name1 in argentina_questions) {
      if (name1 %in% belize_questions) {
        firstlist[[i]] <- name1
        i <- i + 1
      }
    else{
      l[[x]] <- name1
      x <-  x + 1
    }
  }
```


At the end it was really important to makes sure that unique was added because there were a couple of duplicate columns that repeated themselves
```{r}
first <- list_and_list(argentina_questions, bolivia_questions)
second <- list_and_list(first, brazil_questions)
third <- list_and_list(second, belize_questions)
fourth <- list_and_list(third, venezuela_questions)
fifth <- list_and_list(fourth, chile_questions)
sixth <- list_and_list(fifth, colombia_questions)
seven <- list_and_list(sixth, costa_questions)
eigth <- list_and_list(seven, ecuador_questions)
nine <- list_and_list(eigth, elsalvador_questions)
ten <- list_and_list(nine, guatemala_questions)
#eleven <- list_and_list(ten, guyana_questions)
twelve <- list_and_list(ten, paraguay_questions)
thirteen <- list_and_list(twelve, honduras_questions)
#fourteen <- list_and_list(thirteen, jamaica_questions)
fifteen <- list_and_list(thirteen, mexico_questions)
sixteen <- list_and_list(fifteen, nicaragua_questions)
seventeen <- list_and_list(sixteen, panama_questions)
eighteen <- list_and_list(seventeen, peru_questions)
nineteen <- list_and_list(eighteen, suriname_questions)
twenty <- list_and_list(nineteen, usa_questions)
twen_one <- list_and_list(twenty, uruguay_questions)
common_questions <- (list_and_list(twen_one, canada_questions))
unique_questions <- unique(common_questions)
unlist_questions <- (unlist(common_questions))
```










