---
title: "3-Adding Wave Column"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

# Structure
The 2016 and 2017 files are missing the year and wave columns that are present in the merged files. The code below adds the correct wave to the corresponding files.

Note: we use wave instead of year because in some instances the questionnaire is conducted in January of the following year, but is still a part of the previous wave. (e.g. interview is conducted Jan 1, 2005 but wave is 2004)

The countries are first listed by year. There are then functions written for the factored and unfactored versions for both 2016 and 2017 waves. 

And as a reminder, you have to do *both* the factored and unfactored versions.

This step is only required for when individual years need to be combined with a larger merge. Merged datasets should have the wave column.

If your individual years differ from 16/17, you will need to change the name of the datasets and use the correct year in the add wave function.

## Lists of files by year
```{r}
countries_2016 <- list(colombia_16_factor, colombia_16_unfactor, costa_16_factor, costa_16_unfactor, elsalvador_16_factor, elsalvador_16_unfactor, guyana_16_factor, guyana_16_unfactor, honduras_16_factor, honduras_16_unfactor, nicaragua_16_factor, nicaragua_16_unfactor, paraguay_16_factor, paraguay_16_unfactor)
```

We kept the 16 in the object name simply because that is how they were originally loaded in.
```{r}
countries_2017 <- list(argentina_16_factor, argentina_16_unfactor, bolivia_16_factor, bolivia_16_unfactor, brazil_16_factor, brazil_16_unfactor, canada_16_factor, canada_16_unfactor, chile_16_factor, chile_16_unfactor, guatemala_16_factor, guatemala_16_unfactor, jamaica_16_factor, jamaica_16_unfactor, mexico_16_factor, mexico_16_unfactor, peru_16_factor, peru_16_unfactor, usa_16_factor, usa_16_unfactor, uruguay_16_factor, uruguay_16_unfactor)
```

These countries had both 2016 and 2017 in their date column, Ecuador had mainly 2016 while Venezuela had a good number of both 2016 and 2017. For these countries we just decided to use the 2016 function, and make 2016 their default wave column. If this is not what is wanted then you can find them below and change the function that is used from 2016 to the 2017 version.
```{r}
countries_both <- list(ecuador_16_factor, ecuador_16_unfactor, venezuela_16_factor, venezuela_16_unfactor)
```

## Function to adding wave column
### For unfactored datasets
```{r}
add_wave_unfactor_2016 <- function(country){
  #Adds new column, wave, with appropriate year
  country <- country %>%
    mutate(wave = 2016)
  return(country)
}
```

```{r}
add_wave_unfactor_2017 <- function(country){
  #Adds new column, wave, with appropriate year
  country <- country %>%
    mutate(wave = 2017)
  return(country)
}
```

### For factored datasets
```{r}
add_wave_factor_2016 <- function(country){
  #Adds new column, wave, with appropriate year
  country <- country %>%
    mutate(wave_factor = 2016)
  return(country)
}
```

```{r}
add_wave_factor_2017 <- function(country){
  #Adds new column, wave, with appropriate year
  country <- country %>%
    mutate(wave_factor = 2017)
  return(country)
}
```

# 2016 datasets, factored and unfactored
```{r}
#Colombia
colombia_16_factor <- add_wave_factor_2016(colombia_16_factor)
colombia_16_unfactor <- add_wave_unfactor_2016(colombia_16_unfactor)

#Costa Rica
costa_16_factor <- add_wave_factor_2016(costa_16_factor)
costa_16_unfactor <- add_wave_unfactor_2016(costa_16_unfactor)

#Ecuador
ecuador_16_factor <- add_wave_factor_2016(ecuador_16_factor)
ecuador_16_unfactor <- add_wave_unfactor_2016(ecuador_16_unfactor)

#El Salvador
elsalvador_16_factor <- add_wave_factor_2016(elsalvador_16_factor)
elsalvador_16_unfactor <- add_wave_unfactor_2016(elsalvador_16_unfactor)

#Guyana
guyana_16_factor <- add_wave_factor_2016(guyana_16_factor)
guyana_16_unfactor <- add_wave_unfactor_2016(guyana_16_unfactor)

#Honduras
honduras_16_factor <- add_wave_factor_2016(honduras_16_factor)
honduras_16_unfactor <- add_wave_unfactor_2016(honduras_16_unfactor)

#Nicaragua
nicaragua_16_factor <- add_wave_factor_2016(nicaragua_16_factor)
nicaragua_16_unfactor <- add_wave_unfactor_2016(nicaragua_16_unfactor)

#Paraguay
paraguay_16_factor <- add_wave_factor_2016(paraguay_16_factor)
paraguay_16_unfactor <- add_wave_unfactor_2016(paraguay_16_unfactor)
```

# Assumed 2016 wave, factored and unfactored
These are the two that had multiple years, and where if the wave is not the correct one, the function can be changed to make it right
```{r}
#Ecuador
ecuador_16_factor <- add_wave_factor_2016(ecuador_16_factor) 
ecuador_16_unfactor <- add_wave_unfactor_2016(ecuador_16_unfactor)

#Venezuela
venezuela_16_factor <- add_wave_factor_2016(venezuela_16_factor) 
venezuela_16_unfactor <- add_wave_unfactor_2016(venezuela_16_unfactor)
```

# 2017 datasets, factored and unfactored
```{r}
#Argentina
argentina_16_factor <- add_wave_factor_2017(argentina_16_factor)
argentina_16_unfactor <- add_wave_unfactor_2017(argentina_16_unfactor)

#Bolivia
bolivia_16_factor <- add_wave_factor_2017(bolivia_16_factor)
bolivia_16_unfactor <- add_wave_unfactor_2017(bolivia_16_unfactor)

#Brazil
brazil_16_factor <- add_wave_factor_2017(brazil_16_factor)
brazil_16_unfactor <- add_wave_unfactor_2017(brazil_16_unfactor)

#Canada
canada_16_factor <- add_wave_factor_2017(canada_16_factor)
canada_16_unfactor <- add_wave_unfactor_2017(canada_16_unfactor)

#Chile
chile_16_factor <- add_wave_factor_2017(chile_16_factor)
chile_16_unfactor <- add_wave_unfactor_2017(chile_16_unfactor)

#Guatemala
guatemala_16_factor  <- add_wave_factor_2017(guatemala_16_factor)
guatemala_16_unfactor <- add_wave_unfactor_2017(guatemala_16_unfactor) 

#Jamaica
jamaica_16_factor  <- add_wave_factor_2017(jamaica_16_factor) 
jamaica_16_unfactor <- add_wave_unfactor_2017(jamaica_16_unfactor)

#Mexico
mexico_16_factor <- add_wave_factor_2017(mexico_16_factor)
mexico_16_unfactor <- add_wave_unfactor_2017(mexico_16_unfactor)

#Panama
panama_16_factor <- add_wave_factor_2017(panama_16_factor)
panama_16_unfactor <- add_wave_unfactor_2017(panama_16_unfactor)

#Peru
peru_16_factor <- add_wave_factor_2017(peru_16_factor)
peru_16_unfactor <- add_wave_unfactor_2017(peru_16_unfactor)

#United States
usa_16_factor <- add_wave_factor_2017(usa_16_factor)
usa_16_unfactor <- add_wave_unfactor_2017(usa_16_unfactor)

#Uruguay
uruguay_16_factor <- add_wave_factor_2017(uruguay_16_factor) 
uruguay_16_unfactor <- add_wave_unfactor_2017(uruguay_16_unfactor)
```

