---
title: "3-shrinking to common columns"
output: html_notebook
---
This section shrinks each of the dataframes to a shorter width, but we probably won't use this step later and rather use the longer version of our data that we have created

#PART A
```{r}
new_col <- unlist(all_common_col)

shrink <- function(country){
  country <- country[, new_col]
  return(country)
}

```


```{r}
library(purrr)
library(dplyr)

argentina_shrink  <- shrink(argentina)
belize_shrink  <- shrink(belize)
bolivia_shrink  <- shrink(bolivia)
brazil_shrink  <- shrink(brazil)
canada_shrink  <- shrink(canada)
chile_shrink  <- shrink(chile)
colombia_shrink  <- shrink(colombia)
costa_shrink <- shrink(costa)
ecuador_shrink <- shrink(ecuador)
elsalvador_shrink <- shrink(elsalvador)
guatemala_shrink <- shrink(guatemala)
#guyana_shrink <- shrink(guyana) Commented out because it is English-only
honduras_shrink <- shrink(honduras)
#jamaica_shrink <- shrink(jamaica) Commented out because it is English-only
mexico_shrink <- shrink(mexico)
nicaragua_shrink <- shrink(nicaragua)
panama_shrink <- shrink(panama)
paraguay_shrink <- shrink(paraguay)
peru_shrink <- shrink(peru)
suriname_shrink <- shrink(suriname)
usa_shrink <- shrink(usa)
uruguay_shrink <- shrink(uruguay)
venezuela_shrink <- shrink(venezuela)
```


#PART B

```{r}
new_col <- unlist(common_unfactor)

shrink_unfactor <- function(country){
  country <- country[, new_col]
  return(country)
}
```

```{r}
argentina_shrink_unfactor  <- shrink_unfactor(argentina_unfactor)
belize_shrink_unfactor  <- shrink_unfactor(belize_unfactor)
bolivia_shrink_unfactor  <- shrink_unfactor(bolivia_unfactor)
brazil_shrink_unfactor  <- shrink_unfactor(brazil_unfactor)
canada_shrink_unfactor  <- shrink_unfactor(canada_unfactor)
chile_shrink_unfactor <- shrink_unfactor(chile_unfactor)
colombia_shrink_unfactor  <- shrink_unfactor(colombia_unfactor)
costa_shrink_unfactor <- shrink_unfactor(costa_unfactor)
ecuador_shrink_unfactor <- shrink_unfactor(ecuador_unfactor)
elsalvador_shrink_unfactor <- shrink_unfactor(elsalvador_unfactor)
guatemala_shrink_unfactor <- shrink_unfactor(guatemala_unfactor)
#guyana_shrink_unfactor <- shrink_unfactor(guyana_unfactor) Commented out because it is English-only
honduras_shrink_unfactor <- shrink_unfactor(honduras_unfactor)
#jamaica_shrink_unfactor <- shrink_unfactor(jamaica_unfactor) Commented out because it is English-only
mexico_shrink_unfactor <- shrink_unfactor(mexico_unfactor)
nicaragua_shrink_unfactor <- shrink_unfactor(nicaragua_unfactor)
panama_shrink_unfactor <- shrink_unfactor(panama_unfactor)
paraguay_shrink_unfactor <- shrink_unfactor(paraguay_unfactor)
peru_shrink_unfactor <- shrink_unfactor(peru_unfactor)
suriname_shrink_unfactor <- shrink_unfactor(suriname_unfactor)
usa_shrink_unfactor <- shrink_unfactor(usa_unfactor)
uruguay_shrink_unfactor <- shrink_unfactor(uruguay_unfactor)
venezuela_shrink_unfactor <- shrink_unfactor(venezuela_unfactor)
```

```{r}
new_col <- unlist(common_factor)

shrink_factor <- function(country){
  country <- country[, new_col]
  return(country)
}
```

```{r}
argentina_shrink_factor  <- shrink_factor(argentina_factor)
belize_shrink_factor  <- shrink_factor(belize_factor)
bolivia_shrink_factor  <- shrink_factor(bolivia_factor)
brazil_shrink_factor  <- shrink_factor(brazil_factor)
canada_shrink_factor  <- shrink_factor(canada_factor)
chile_shrink_factor  <- shrink_factor(chile_factor)
colombia_shrink_factor  <- shrink_factor(colombia_factor)
costa_shrink_factor <- shrink_factor(costa_factor)
ecuador_shrink_factor <- shrink_factor(ecuador_factor)
elsalvador_shrink_factor <- shrink_factor(elsalvador_factor)
guatemala_shrink_factor <- shrink_factor(guatemala_factor)
#guyana_shrink_factor <- shrink_factor(guyana_factor) Commented out because it is English-only
honduras_shrink_factor <- shrink_factor(honduras_factor)
#jamaica_shrink_factor <- shrink_factor(jamaica_factor) Commented out because it is English-only
mexico_shrink_factor <- shrink_factor(mexico_factor)
nicaragua_shrink_factor <- shrink_factor(nicaragua_factor)
panama_shrink_factor <- shrink_factor(panama_factor)
paraguay_shrink_factor <- shrink_factor(paraguay_factor)
peru_shrink_factor<- shrink_factor(peru_factor)
suriname_shrink_factor <- shrink_factor(suriname_factor)
usa_shrink_factor <- shrink_factor(usa_factor)
uruguay_shrink_factor <- shrink_factor(uruguay_factor)
venezuela_shrink_factor <- shrink_factor(venezuela_factor)
```


#For reference only

Don't use this, just want to keep track of what we tried

These things below were what we were trying to create in order to only have the common questions as the colummn headers, but this got more complicated as we found that there were duplicate column questions, which caused the countries not to shrink properly or recombine properly

Use this shrink if goin to do join on countries.... need to only allow in unique ones
```{r}
shrink2 <- function(country){
  y <- 1
  x <- 1
  new_col <- rep(NA, 128)
  columns <- attributes(country)$names
  while(x <= length(columns)){
    d <- (attributes(country[[columns[x]]]))$label
    if(is.null(d) == FALSE){
      if(d %in% common_questions){
        new_col[y] <- columns[x]
        y <- y + 1
      }
    }
    x <-  x + 1
  }
  new_col <- unlist(new_col)
  arg_test <- country[ ,new_col]
}

```

Need to try to make unique columns only, add to list and then make happen
```{r}
shrink2 <- function(country){
  y <- 1
  x <- 1
  new_col <- rep(NA, 128)
  columns <- attributes(country)$names
  while(x <= length(columns)){
    d <- (attributes(country[[columns[x]]]))$label
    if(is.null(d) == FALSE){
      if(d %in% common_questions){
        new_col[y] <- columns[x]
        y <- y + 1
      }
    }
    x <-  x + 1
  }
  new_col <- unlist(new_col)
  arg_test <- country[ ,new_col]
}

```



```{r}
argentina_shrinkx  <- shrink2(argentina)
belize_shrinkx  <- shrink2(belize)
bolivia_shrinkx  <- shrink2(bolivia)
brazil_shrinkx  <- shrink2(brazil)
canada_shrinkx  <- shrink2(canada)
chile_shrinkx <- shrink2(chile)
colombia_shrinkx  <- shrink2(colombia)
costa_shrinkx <- shrink2(costa)
ecuador_shrinkx <- shrink2(ecuador)
elsalvador_shrinkx <- shrink2(elsalvador)
guatemala_shrinkx <- shrink2(guatemala)
#guyana_shrinkx <- shrink2(guyana) Commented out because it is English-only
honduras_shrinkx <- shrink2(honduras)
#jamaica_shrinkx <- shrink2(jamaica) Commented out because it is English-only
mexico_shrinkx <- shrink2(mexico)
nicaragua_shrinkx <- shrink2(nicaragua)
panama_shrinkx <- shrink2(panama)
paraguay_shrinkx <- shrink2(paraguay)
peru_shrinkx <- shrink2(peru)
suriname_shrinkx <- shrink2(suriname)
usa_shrinkx <- shrink2(usa)
uruguay_shrinkx <- shrink2(uruguay)
venezuela_shrinkx <- shrink2(venezuela)
```
