---
title: "5-Lengthening and Joining"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

# Structure
In this document, we lengthened all of the data frames we created before, combined the 2016/17 datasets with their respecitve factored and unfactored versions, and merged the unfactored and factored versions together.

Lengthening the data frames allows for us to put the data in a tidy format. Tidy data is a way of organizing data that makes it easy to visualize. This was developed by Hadley Wickham, and you can read more about tidy data [here](https://vita.had.co.nz/papers/tidy-data.pdf). When we simply read in the datasets, there are hundreds of columns, but by lengthening the data frame, we narrow the column down to five and it is easier to manage.

## Functions to lengthen unfactored versions
The first thing that we do is create a long, tidy version of the data. This makes it easier to filter and select what we want later on. We gathered the data so that "column_name" would have all the column names and "answer" would have all the observations to the corresponding column name.

Then, we transformed answer to a character which is necessary for the later combination with the 2016/17 data frame. If you are not merging, you *do not* need to transform the answer column.

Finally, we select the five columns that we want.


### For merged unfactored datasets
```{r}
lengthen <- function(country) {
  #makes sure the weight is saved
  weight <- country %>%
    select(weight1500)
  weight <- weight %>% rename(weights = weight1500)
    #Brings together the following columns
  country <- bind_cols(country,weight)
  country <- country %>%
    gather(column_name, answer_measure, estratopri:formatq)
  #Necessary when joining with 16/17
  country <- transform(country, answer_measure = as.character(answer_measure))
  #Selects the columns we want
  country <- country %>% 
    select(pais, wave, uniq_id, column_name, answer_measure, weights)
  return(country)
}
```

### For 16/17 unfactored datasets.
```{r}
lengthen_16 <- function(country) {
  #makes sure the weight is saved
  weight <- country %>%
    select(wt)
  weight <- weight %>% rename(weights = wt)
    #Brings together the following columns
  country <- bind_cols(country,weight)
  country <- country %>%
    #Brings together the following columns
    gather(column_name, answer_measure, estratopri:formatq)
  
  #Necessary when joining with merged files
  country <- transform(country, answer_measure = as.character(answer_measure))
  
  #Selects the columns we want
  country <- country %>% 
    select(pais, wave, uniq_id, column_name, answer_measure, weights)
  return(country)
}
```

## Functions to lengthen factored versions
These functions are almost identical to the ones above except, they have "_factor" for the column names.
### For merged, factored datasets
```{r}
lengthen_factor <- function(country) {
  #makes sure the weight is saved
  weight <- country %>%
    select(weight1500_factor)
 weight <- weight %>% rename(weights_factor = weight1500_factor)
    #Brings together the following columns
  country <- bind_cols(country,weight)
  country <- country %>%
    #Brings together the following columns
    gather(column_name_factor, answer_dimension, estratopri_factor:formatq_factor)
  
  #Selects columns that we want
  country <- country %>% 
    select(pais_factor, wave_factor, uniq_id_factor, column_name_factor, answer_dimension, weights_factor)
  return(country)
}
```

### For 2016/17 factored datasets
```{r}
lengthen_16factor <- function(country) {
  #makes sure the weight is saved
  weight <- country %>%
    select(wt_factor)
  weight <- weight %>% rename(weights_factor = wt_factor) %>% transform(weights_factor = as.numeric(weights_factor))
    #Brings together the following columns
  country <- bind_cols(country,weight)
  country <- country %>%
    #Brings together the following columns
    gather(column_name_factor, answer_dimension, estratopri_factor:formatq_factor)
  
  #Selects columns that we want
  country <- country %>% 
    select(pais_factor, wave_factor, uniq_id_factor, column_name_factor, answer_dimension, weights_factor)
  return(country)
}
```

#Connects the category and question excel to the dataframes
```{r}
factor_add <- function(country){
  #uses left joins to bring together the excel doc and dataframe based on column name
  country <- country %>%
  left_join(factored_questions, by = 'column_name_factor') %>%
  left_join(factored_categories, by = 'column_name_factor')
  return(country)
}
```

#Connects the category and question excel to the dataframes
```{r}
unfactor_add <- function(country){
  #uses left joins to bring together the excel doc and dataframe based on column name
  country <- country %>%
  left_join(unfactored_questions, by = 'column_name') %>%
  left_join(unfactored_categories, by = 'column_name')
  return(country)
}
```

# Creating a list of unwated variables
These variables are not to be shown in the visualizations, so in order to remove them from the datasets above, we created a vector with the variable names that will then be applied to a function that removes them.

If in the future you want to remove more variables, just add them to the list and run the same function.

```{r}
variables <- c('ls3r', 'a4r', 'cp4ar', 'np1r', 'np2r', 'prot3r', 'prot7r', 'jc15ar', 'vic1extr', 'vic1hogarr',
'jc10rr', 'jc13rr', 'sgl1r', 'm1r', 'cp5r', 'cp6r', 'cp7r', 'cp8r', 'cp9r', 'cp13r', 'cp20r', 'it1r', 'pn4r', 'pol1r', 'exc7r', 'community' ,'anyvictim', 'aoj11r', 'sd2r', 'sd3r', 'sd6r', 'coupr', 'b1r', 'b2r', 'b3r', 'b4r', 'b6r', 'b12r', 'b32r','n11r', 'n9r', 'mil3r', 'mil4r', 'eff1r', 'eff2r', 'mil7r', 'ing4r', 'ros1r', 'ros4r', 'psar', 'psa5r', 'psa2r', 'd1r', 'd2r', 'd3r', 'd4r', 'd5r', 'tolr', 'tol2r','bar2x2', 'exc2r', 'exc6r', 'ecexc11r', 'exc11r', 'exc13r', 'exc14r', 'exc15r', 'exc16r', 'exc20r', 'exctot', 'exctot5r', 'exctot3r', 'corvic', 'vb2r', 'mujer', 'edr', 'edad', 'age1', 'age2', 'age3', 'age4', 'age5', 'age6', 'q5br', 'q10dr', 'housewife', 'etidr', 'indigenous', 'black', 'white', 'mestizo', 'mulatto', 'other', 'quintall', 'ed2r', 'intid', 'ideology', 'ti', 'q11nr', 'q5bnr')
```

# Final clean
This function uses the list made above to remove the desire variables. It also further formats the data frame into the shape it needs to be when we bind all the countries together.
```{r}
clean <- function(country){
  #Filters out the column names that are not in the list, variables.
  country <- country %>%
   filter(!(column_name %in% variables)) %>%
    #Selects the columns that are no longer needed
    select(-wave_factor, -uniq_id, -column_name, -column_name_factor, -question_factor, -weights_factor) %>% 
    #Renames pais_factor to country
    rename(country = pais_factor)
  return(country)
}
```

#Unmerged combination
This function takes in the unfactored version for before 2016 as well as after. It takes each dataframe, lengthens it, adds the unfactored versions to each other, and the factored versions to each other. Then it filters out the NAs from both, and combines them togehter. For the majority of each step there is a call to a function written above.
```{r}
unmerged <- function(unfactor, unfactor16, factor, factor16){
  #lengthens all dataframes through above wrtten lengthen functions
  unfactor <- lengthen(unfactor)
  unfactor16 <- lengthen_16(unfactor16)
  factor <- lengthen_factor(factor)
  factor16 <- lengthen_16factor(factor16)
  
  #brings unfactored and factored seperated date dataframes together
  unfactor_plus <- union_all(unfactor,unfactor16) %>% 
    transform(answer_measure = as.numeric(answer_measure)) 
  factor_plus <- union_all(factor,factor16)
  
  #gets rid of the NAs, and adds the category and question column by above written functions 
  unfactor_plus <- unfactor_add(unfactor_plus) %>%
    filter(is.na(category) == FALSE)
  factor_plus <- factor_add(factor_plus) %>%
    filter(is.na(category) == FALSE)
  
  #finally combines the unfactor and factor using bind_cols
  unfactor_plus <- unfactor_plus %>% select(-category)
  complete <- bind_cols(factor_plus, unfactor_plus)  %>%
    transform(answer_measure = as.numeric(answer_measure))
  
  #cleans the final version with above written function
  complete <- clean(complete)
  
}
```

#Merged combination
Similar to the above function, but this is used when there is no need to merge other dataframes together from multiple years
```{r}
merged <- function(unfactor, factor){
  #lengthens all dataframes through above wrtten lengthen functions
  unfactor <- lengthen(unfactor)
  factor <- lengthen_factor(factor)
  
  #gets rid of the NAs, and adds the category and question column by above written functions 
  unfactor <- unfactor_add(unfactor) %>%
    filter(is.na(category) == FALSE)
  factor <- factor_add(factor) %>%
    filter(is.na(category) == FALSE)

  #finally combines the unfactor and factor using bind_cols
  unfactor <- unfactor %>% select(-category)
  complete <- bind_cols(factor, unfactor)  %>%
    transform(answer_measure = as.numeric(answer_measure))
  
  #cleans the final version with above written function
  complete <- clean(complete)
}
```


```{r}
argentina_clean <- unmerged(argentina_unique_unfactor, argentina_16_unfactor, argentina_unique_factor, argentina_16_factor)
belize_clean <- merged(belize_unique_unfactor, belize_unique_factor)
brazil_clean <- unmerged(brazil_unique_unfactor, brazil_16_unfactor, brazil_unique_factor, brazil_16_factor)
chile_clean <- unmerged(chile_unique_unfactor, chile_16_unfactor, chile_unique_factor, chile_16_factor)
panama_clean <- unmerged(panama_unique_unfactor, panama_16_unfactor, panama_unique_factor, panama_16_factor)
paraguay_clea <- unmerged(paraguay_unique_unfactor, paraguay_16_unfactor, paraguay_unique_factor, paraguay_16_factor)
peru_clean <- unmerged(peru_unique_unfactor, peru_16_unfactor, peru_unique_factor, peru_16_factor)
uruguay_clean <- unmerged(uruguay_unique_unfactor, uruguay_16_unfactor, uruguay_unique_factor, uruguay_16_factor)
venezuela_clean <- unmerged(venezuela_unique_unfactor, venezuela_16_unfactor, venezuela_unique_factor, venezuela_16_factor)
bolivia_clean <- unmerged(bolivia_unique_unfactor, bolivia_16_unfactor, bolivia_unique_factor, bolivia_16_factor)
canada_clean <- unmerged(canada_unique_unfactor, canada_16_unfactor, canada_unique_factor, canada_16_factor)
colombia_clean <- unmerged(colombia_unique_unfactor, colombia_16_unfactor, colombia_unique_factor, colombia_16_factor)
costa_clean <- unmerged(costa_unique_unfactor, costa_16_unfactor, costa_unique_factor, costa_16_factor)
ecuador_clean <- unmerged(ecuador_unique_unfactor, ecuador_16_unfactor, ecuador_unique_factor, ecuador_16_factor)
elsalvador_clean <- unmerged(elsalvador_unique_unfactor, elsalvador_16_unfactor, elsalvador_unique_factor, elsalvador_16_factor)
guatemala_clean <- unmerged(guatemala_unique_unfactor, guatemala_16_unfactor, guatemala_unique_factor, guatemala_16_factor)
honduras_clean <- unmerged(honduras_unique_unfactor, honduras_16_unfactor, honduras_unique_factor, honduras_16_factor)
mexico_clean <- unmerged(mexico_unique_unfactor, mexico_16_unfactor, mexico_unique_factor, mexico_16_factor)
nicaragua_clean <- unmerged(nicaragua_unique_unfactor, nicaragua_16_unfactor, nicaragua_unique_factor, nicaragua_16_factor)
usa_clean <- unmerged(usa_unique_unfactor, usa_16_unfactor, usa_unique_factor, usa_16_factor)
suriname_clean <- merged(suriname_unique_unfactor, suriname_unique_factor)
guyana_clean <- unmerged(guyana_unique_unfactor, guyana_16_unfactor, guyana_unique_factor, guyana_16_factor)
jamaica_clean <- unmerged(jamaica_unique_unfactor, jamaica_16_unfactor, jamaica_unique_factor, jamaica_16_factor)
```


# Combining and choosing
In order to write a .csv file of the data, we combined all the countries using `bind_rows()` and saved it in a data frame called complete. However, because Tableau Public can only handle 15 million rows, we subset the data by filtering out for when wave is 2006, 2008, 2010, and 2012 and used this data frame to write the .csv.

We also removed the countries and their specific years that are not public. If you want to show some of them just remove or comment out the line. If you want to remove more countries and years, just use the same format shown below.

```{r}
#Combines all the datasets into single data frame
complete <- bind_rows(belize_clean, argentina_clean, brazil_clean, chile_clean, panama_clean, paraguay_clean, peru_clean, uruguay_clean, venezuela_clean, bolivia_clean, canada_clean, colombia_clean, costa_clean, ecuador_clean, elsalvador_clean, guatemala_clean, honduras_clean, mexico_clean, nicaragua_clean, usa_clean, suriname_clean, guyana_clean, jamaica_clean)

complete <- complete %>% 
  filter(!(pais == 41 & wave > 2008)) %>%
  filter(!(pais == 40 & wave > 2008)) %>%
  filter(!(pais == 16 & wave > 2008)) %>%
  filter(!(pais == 13 & wave > 2008)) %>%
  filter(!(pais == 17 & wave > 2008)) %>%
  filter(!(pais == 10 & wave > 2008)) %>%
  filter(!(pais == 27 & wave > 2008 & wave < 2014)) %>%
  filter(!(pais == 35 & wave > 2008 & wave < 2014)) %>%
  filter(!(pais == 9 & wave < 2014))

```

```{r}
test2 <- complete %>% filter(wave < 2014)
test3 <- complete %>% filter(wave > 2014)

write_csv(complete, "t.csv")
write_csv(test2, "test2.csv")
write_csv(test3, "test3.csv")
```



