---
title: "6-Subsetting Categories"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

# Structure of code
This creates subsets of the categories to hopefully work around the row limit in Tableau Public. We created these groups based on similarities between the kinds of questions asked.

## Groups
1. Politics
2. Institutions
3. Interpersonal
4. Individual

### Politics
These categories ask questions related to political beliefs and political leanings.
```{r}
politics <- list("The Economy", "Civic and Political Engagement", "Political/Electoral Engagement", "Foreign Relations")
```

### Institutions
List of categories that ask about perception of institutions in their country.
```{r}
institutions <- list("Local Government", "Evaluation of Institutions, Political System, and Other Persons", "Support for Democracy and Democratic Institutions", "Corruption")
```

### Interpersonal
List of categories that deal with interpersonal conflicts.
```{r}
interpersonal <- list("Crime, Insecurity, and Policy Preferences", "Political Tolerance", "Migration", "Gender", "Social Media")
```

### Individual
These categories ask questions regarding information on the individual level.
```{r}
individual <- list("Climate Change/Disaster Risk Reduction", "Political and Religious Orientation", "Sample Identification/Geographic", "Socio-Demographic Characteristics")
```



