---
title: "putting l1 first"
output: html_notebook
---
This moves l1 to the front of the datatable so that when we use it to do machiene learning and data prediction we can easily access it. I chose l1 because it is asking where they lie on the political spectrum, which I thought would be something interesting to analyze. *But just talked to Jesse and he said that we should do something more like "how safe do you feel" because that will be something that we can easily find data on and compare what we find to. 

To change it to do this for other questions - and finding a question about safety - I would go through the common questions that can be created in file 2-common columns, and then look at the questions and choose one that seems most similar to something about safety, and from there just finding what the column name is and replacing l1 in the function with that column name


I ran this after the read in(did the unfactored), and then did then added the unique id to the end in part 4 - and then wrote Argentina to a csv file from there i played around with it a little bit in H20(an online application that is used for machiene learning/AI - and i forwarded you the info to set it up) when I read it in and parsed it I didn't change any variables, and then split it(labeling training to the .75 and modeling to .25), and tested out a couple of different modeling types with l1 as the response column, and chose to do 5 folds. When I tested it the R2 was less that .2 - which I'm pretty sure isn't good lol, but Jesse said is actually ok for political sciences stuff

But I also did some general research on Argentina and its political system, which has got a lot going on. I didn't find any other specific data about people expressing their own political leanings but I'm sure that it's out there. Jesse said that finding other data to compare it to could allow us to help LAPOP and potentially give them recomendations - which will probs be even easier to find for safety questions

Also they gave us access to the files on box, and I was looking into packages on R to be able to pull it in, but Jesse said that we just need to download them from box, so I guess not really do anything differently from what we did before. But I would just talk about that in the meeting tomorrow and how it'll change the way that we work, because there are like 48 files in the box
```{r}
reshape <- function(country){
  start <- country %>% select(l1)
  end <- country %>% select(-l1)
  final <- cbind(start,end)
  final
}
```

```{r}
argentina_reshape  <- reshape(argentina_unfactor)
belize_reshape  <- reshape(belize_unfactor)
bolivia_reshape  <- reshape(bolivia_unfactor)
brazil_reshape  <- reshape(brazil_unfactor)
canada_reshape  <- reshape(canada_unfactor)
chile_reshape  <- reshape(chile_unfactor)
colombia_reshape  <- reshape(colombia_unfactor)
costa_reshape <- reshape(costa_unfactor)
ecuador_reshape <- reshape(ecuador_unfactor)
elsalvador_reshape <- reshape(elsalvador_unfactor)
guatemala_reshape <- reshape(guatemala_unfactor)
guyana_reshape <- reshape(guyana_unfactor) 
honduras_reshape <- reshape(honduras_unfactor)
jamaica_reshape <- reshape(jamaica_unfactor) 
mexico_reshape <- reshape(mexico_unfactor)
nicaragua_reshape <- reshape(nicaragua_unfactor)
panama_reshape <- reshape(panama_unfactor)
paraguay_reshape <- reshape(paraguay_unfactor)
peru_reshape <- reshape(peru_unfactor)
suriname_reshape <- reshape(suriname_unfactor)
usa_reshape <- reshape(usa_unfactor)
uruguay_reshape <- reshape(uruguay_unfactor)
venezuela_reshape <- reshape(venezuela_unfactor)
```




