---
title: "Testing Wide Unique ID"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

# Structure
I am testing to ensure that the person ID is unique. This affects the data later on.

```{r}
library(assertr)
library(purrr)
```


## Asserts
Going to check them individually
```{r}
#Successful
argentina_unique_unfactor %>% 
  assert(is_uniq, person_id)
#Successful
belize_unique_unfactor%>% 
  assert(is_uniq, person_id)
```

Making a function for it
```{r}
check_unique <- function(country) {
  country %>% 
    assert(is_uniq, person_id)
}
```

```{r}
unfactored_countries <- list(argentina_unique_unfactor, belize_unique_unfactor, bolivia_unique_unfactor, brazil_unique_unfactor, canada_unique_unfactor, chile_unique_unfactor, colombia_unique_unfactor, costa_unique_unfactor, ecuador_unique_unfactor, elsalvador_unique_unfactor, guatemala_unique_unfactor, guyana_unique_unfactor, honduras_unique_unfactor, jamaica_unique_unfactor, mexico_unique_unfactor, nicaragua_unique_unfactor, panama_unique_unfactor, paraguay_unique_unfactor, peru_unique_unfactor, suriname_unique_unfactor, usa_unique_unfactor, uruguay_unique_unfactor, venezuela_unique_unfactor)
```

```{r}
map(unfactored_countries, check_unique)
```

Okay so it says that an issue starts at 1004, but person_id violates the assertion is_uniq 377 times, so we've got to find that. Going to check individually again.

```{r}
#Failed - 377 times
check_unique(bolivia_unique_unfactor)
#Successful!
check_unique(brazil_unique_unfactor)
#Failed - 70 times
check_unique(canada_unique_unfactor)
#Successful!
check_unique(chile_unique_unfactor)
#Failed - 4 times
check_unique(colombia_unique_unfactor)
#Failed - 4496 times
check_unique(costa_unique_unfactor)
#Failed - 4 times
check_unique(ecuador_unique_unfactor)
#Failed - 96 times
check_unique(elsalvador_unique_unfactor)
#Failed - 8 times
check_unique(guatemala_unique_unfactor)
#Successful!
check_unique(guyana_unique_unfactor)
#Failed - 5 times
check_unique(honduras_unique_unfactor)
#Failed - 4 times
check_unique(jamaica_unique_unfactor)
#Failed - 1134 times
check_unique(mexico_unique_unfactor)
#Failed - 2 times
check_unique(nicaragua_unique_unfactor)
#Successful!
check_unique(panama_unique_unfactor)
#Successful!
check_unique(paraguay_unique_unfactor)
#Successful!
check_unique(peru_unique_unfactor)
#Successful!
check_unique(suriname_unique_unfactor)
#Successful!
check_unique(usa_unique_unfactor)
#Successful!
check_unique(uruguay_unique_unfactor)
#Successful!
check_unique(venezuela_unique_unfactor)
```

Unfactored countries that are verified as unique:
Argentina, Belize, Brazil, Chile, Guyana, Panama, Paraguay, Peru, Suriname, USA, Uruguay, Venezuela

## Asserting with factored countries

```{r}
factored_countries <- list(argentina_unique_factor, belize_unique_factor, bolivia_unique_factor, brazil_unique_factor, canada_unique_factor, chile_unique_factor, colombia_unique_factor, costa_unique_factor, ecuador_unique_factor, elsalvador_unique_factor, guatemala_unique_factor, guyana_unique_factor, honduras_unique_factor, jamaica_unique_factor, mexico_unique_factor, nicaragua_unique_factor, panama_unique_factor, paraguay_unique_factor, peru_unique_factor, suriname_unique_factor, usa_unique_factor, uruguay_unique_factor, venezuela_unique_factor)
```

```{r}
check_unique_factor <- function(country) {
  country %>% 
    assert(is_uniq, person_id_factor)
}
```

```{r}
map(factored_countries, check_unique_factor)
```

Ran into the same issue as above, so going to check individual countries
```{r}
#Successful!
check_unique_factor(argentina_unique_factor)
#Successful!
check_unique_factor(belize_unique_factor)
#Failed
check_unique_factor(bolivia_unique_factor)
#Successful!
check_unique_factor(brazil_unique_factor)
#Failed - 70 times
check_unique_factor(canada_unique_factor)
#Successful!
check_unique_factor(chile_unique_factor)
#Failed - 4 times
check_unique_factor(colombia_unique_factor)
#Failed - 4496 times
check_unique_factor(costa_unique_factor)
#Failed - 4 times
check_unique_factor(ecuador_unique_factor)
#Failed - 96 times
check_unique_factor(elsalvador_unique_factor)
#Failed - 8 times
check_unique_factor(guatemala_unique_factor)
#Successful!
check_unique_factor(guyana_unique_factor)
#Failed - 2 times - DIFFERENT FROM UNFACTORED
check_unique_factor(honduras_unique_factor)
#Failed - 4 times
check_unique_factor(jamaica_unique_factor)
#Failed - 1134 times
check_unique_factor(mexico_unique_factor)
#Failed - 2 times
check_unique_factor(nicaragua_unique_factor)
#Successful!
check_unique_factor(panama_unique_factor)
#Successful!
check_unique_factor(paraguay_unique_factor)
#Successful!
check_unique_factor(peru_unique_factor)
#Successful!
check_unique_factor(suriname_unique_factor)
#Successful!
check_unique_factor(usa_unique_factor)
#Successful!
check_unique_factor(uruguay_unique_factor)
#Successful!
check_unique_factor(venezuela_unique_factor)
```

These end up pretty much with the same results as aboved except Honduras only has 2 repeats instead of five. Not sure what's up with that.

## Testing the 2016 waves
All of the datasets from the 2016 waves are unique.
```{r}
#Argentina
check_unique_factor(argentina_16_factor)
check_unique(argentina_16_unfactor)

#Bolivia
check_unique_factor(bolivia_16_factor)
check_unique(bolivia_16_unfactor)

#Brazil
check_unique_factor(brazil_16_factor)
check_unique(brazil_16_unfactor)

#Canada
check_unique_factor(canada_16_factor)
check_unique(canada_16_unfactor)

#Chile
check_unique_factor(chile_16_factor)
check_unique(chile_16_unfactor)

#Colombia
check_unique_factor(colombia_16_factor)
check_unique(colombia_16_unfactor)

#Costa Rica
check_unique_factor(costa_16_factor)
check_unique(costa_16_unfactor)

#Ecuador
check_unique_factor(ecuador_16_factor)
check_unique(ecuador_16_unfactor)

#El Salvador
check_unique_factor(elsalvador_16_factor)
check_unique(elsalvador_16_unfactor)

#Guatemala
check_unique_factor(guatemala_16_factor)
check_unique(guatemala_16_unfactor) 

#Guyana
check_unique_factor(guyana_16_factor)
check_unique(guyana_16_unfactor)

#Honduras
check_unique_factor(honduras_16_factor)
check_unique(honduras_16_unfactor)

#Jamaica
check_unique_factor(jamaica_16_factor) 
check_unique(jamaica_16_unfactor)

#Mexico
check_unique_factor(mexico_16_factor)
check_unique(mexico_16_unfactor)

#Nicaragua
check_unique_factor(nicaragua_16_factor)
check_unique(nicaragua_16_unfactor)

#Panama
check_unique_factor(panama_16_factor)
check_unique(panama_16_unfactor)

#Paraguay
check_unique_factor(paraguay_16_factor)
check_unique(paraguay_16_unfactor)

#Peru
check_unique_factor(peru_16_factor)
check_unique(peru_16_unfactor)

#United States
check_unique_factor(usa_16_factor)
check_unique(usa_16_unfactor)

#Uruguay
check_unique_factor(uruguay_16_factor) 
check_unique(uruguay_16_unfactor)

#Venezuela
check_unique_factor(venezuela_16_factor) 
check_unique(venezuela_16_unfactor)
```